Measuring precise radial velocities and cross-correlation function line-profile variations using a Skew Normal density \thanks{Based on observations collected at the La Silla Parana Observatory, ESO (Chile), with the HARPS spectrograph at the 3.6-m telescope.}

### 2018-05-31 manuscript.tex
sec 3 updates

In order to show the goodness of this correction, a statistical test on the parameters $\beta_{0}$, $\beta_{1}$, $\beta_{2}$, $\beta_{3}$ and $\beta_{4}$ is presented, where the null hypothesis is $H_{0}: \beta_{i}=0$, for $i=0,\dots,4$. The level for not rejecting the null hypothesis is fixed to $0.05$. The coefficient of multiple correlation $R^2$ is introduced in order to explain how well this linear combination addresses the variability of the RV variation induced by stellar activity.

>>>>

The proposed model is analyzed using statistical tests on the parameters $\beta_{0}$, $\beta_{1}$, $\beta_{2}$, $\beta_{3}$ and $\beta_{4}$ where the null hypothesis is $H_{0}: \beta_{i}=0$, for $i=0,\dots,4$. The significance level for the tests are set at $0.05$. The coefficient of determination, $R^2$, is used to assess how well the proposed linear combination of variables accounts for the variability of $RV_{\text{activity}}$.
